Evolution of a conspicuous dynamic visual signal in an introduced chameleon

### 2021-04-23 ms.Rmd
Adding some sub-headings to make it easier to follow. I worry a little still about non-independence within individuals, so also added code to do sensitivity analysis which uses Robust Variance Estaimtors and small sample corrections to esatimte SEs correctly

```{r Models, echo = FALSE, results = "hide"}
#########################################################
# Male-male Competition Displays
#########################################################
#Load data and clean a bit
Display_1 <- read.table("./data/Display_1.csv", 
                          header=TRUE, sep=",", dec=".", strip.white=TRUE)

@@

# Display dl
    ConspicDisplayAC <- lmer(dL ~ sc_SVL + Population + (1|ID), data=Display_1)
    summary(ConspicDisplayAC)
    coefAIC_display = fixef(ConspicDisplayAC)[3]
    CI_AC_display <- data.frame(confint(ConspicDisplayAC))
    anovaConspicDisplayAC <- anova(ConspicDisplayAC)

## Display dS
         ConspicDisplayCC <- lmer(dS ~ sc_SVL + Population + (1|ID), data=Display_1)
    anovaConspicDisplayCC <- anova(ConspicDisplayCC)

#########################################################
# Courtship Displays
#########################################################

@@

# Courtship dl
ConspicCourtshipAC <- lmer(dL ~ sc_SVL + Population  + (1|ID), data=Courtship)
summary(ConspicCourtshipAC)
coefAIC_court = fixef(ConspicCourtshipAC)[3]
CI_AC_court <- data.frame(confint(ConspicCourtshipAC))
courship_anovaAC <- anova(ConspicCourtshipAC)

# Courtship dS
  ConspicCourtshipCC <- lmer(dS ~ sc_SVL + Population  + (1|ID), data=Courtship)
 courship_anovaCC <- anova(ConspicCourtshipCC)

 #########################################################
# Displays to Predators, birds and snake
#########################################################
 Predator <- read.table("./data/Predator_2_3.csv", 
                       header=TRUE, sep=",", dec=".", strip.white=TRUE)

@@

# Transformation
Predator <- Predator %>% mutate(log_dS = log(dS),
                                log_dL = log(dL),
                                sqrt_dS = sqrt(dS),
                                sqrt_dL = sqrt(dL))

# Models - Achromatic Contrast (dL)

@@

# No support for an interaction, so can drop interaction. Tells us that predation, regardless of whether we are talking snake or bird is just low in Hawaii, otherwise, we would predict that signals would evolve to match the predatory system 
PredatorAC <- lmer(dL ~ Predator + Population + (1|ID), data = Predator) 
summary(PredatorAC)
anova_predators <- anova(PredatorAC)

# Chromatic contrast - dS

PredatorCC <- lmer(dS ~ Predator + Population + Predator:Population + (1|ID), data = Predator) 
summary(PredatorCC)
anova_predators_interCC <- anova(PredatorCC)

@@

@@

Sexual selection is expected to favour more conspicuous dymamic sexual signals in Hawaii under relaxed predation because higher predation should favour cryptic signals whereas greater conspicuousness of sexual signals should be selected in social contexts. In support of this prediction, male display colouration exhibited in social contexts (i.e., male-male contests and courtship) was more conspicuous to a conspecific in Hawaii compared with Kenya (**Male-Male Contests**: Acromatic contrast ($dl$); $F_{`r anovaConspicDisplayAC$NumDF[2]`,`r anovaConspicDisplayAC$DenDF[2]`}$ = `r anovaConspicDisplayAC[5][2,]`, p = `r p_value(anovaConspicDisplayAC[6][2,])`; Chromatic contrast ($dS$): $F_{`r anovaConspicDisplayCC$NumDF[2]`,`r anovaConspicDisplayCC$DenDF[2]`}$ = `r anovaConspicDisplayCC[5][2,]`, p = `r p_value(anovaConspicDisplayCC[6][2,])`; **Courtship displays**: Acromatic contrast ($dl$); $F_{`r courship_anovaAC$NumDF[2]`,`r courship_anovaAC$DenDF[2]`}$ = `r courship_anovaAC[5][2,]`, p = `r p_value(courship_anovaAC[6][2,])`; Chromatic contrast ($dS$): $F_{`r courship_anovaCC$NumDF[2]`,`r courship_anovaCC$DenDF[2]`}$ = `r courship_anovaCC[5][2,]`, p = `r p_value(courship_anovaCC[6][2,])`), and this was  true across all body regions measured (See Supplemental Materials, table S1). Kenyan chameleons were significantly more crypic compared to introduced Hawaiian counterparts (Acromatic Contrast between Hawaiian and Kenyan Populations, Male-male contests: $\beta$ = `r coefAIC_display`, 95% CI = `r CI_AC_display[5,1]` to  `r CI_AC_display[5,2]`, df = `r summary(ConspicDisplayAC)$coefficients[3, "df"]`, t =  `r summary(ConspicDisplayAC)$coefficients[3, "t value"]`, p = `r p_value(summary(ConspicDisplayAC)$coefficients[3, "Pr(>|t|)"])`, Courtship: $\beta$ = `r coefAIC_court`, 95% CI = `r CI_AC_court[5,1]` to  `r CI_AC_court[5,2]`, df = `r summary(ConspicCourtshipAC)$coefficients[3, "df"]`, t =  `r summary(ConspicCourtshipAC)$coefficients[3, "t value"]`, p = `r p_value(summary(ConspicCourtshipAC)$coefficients[3, "Pr(>|t|)"])`, see figure 1a & b).

@@

@@

>>>>

```{r Models, echo = FALSE, results = "hide"}
#########################################################
# Social Context: Male-male Competition Displays
#########################################################
#Load data and clean a bit
Display_1 <- read.table("./data/Display_1.csv", 
                          header=TRUE, sep=",", dec=".", strip.white=TRUE)

@@

##########
## Achromatic Contrast - dL
##########
    ConspicDisplayAC <- lmer(dL ~ sc_SVL + Population + (1|ID), data=Display_1)
    summary(ConspicDisplayAC)
    coefAIC_display = fixef(ConspicDisplayAC)[3]
    CI_AC_display <- data.frame(confint(ConspicDisplayAC))
    anovaConspicDisplayAC <- anova(ConspicDisplayAC)

##########
# Chromatic contrast - dS
##########
         ConspicDisplayCC <- lmer(dS ~ sc_SVL + Population + (1|ID), data=Display_1)
    anovaConspicDisplayCC <- anova(ConspicDisplayCC)

#########################################################
# Social Context: Courtship Displays
#########################################################

@@

##########
## Achromatic Contrast - dL
##########
ConspicCourtshipAC <- lmer(dL ~ sc_SVL + Population  + (1|ID), data=Courtship)
summary(ConspicCourtshipAC)
coefAIC_court = fixef(ConspicCourtshipAC)[3]
CI_AC_court <- data.frame(confint(ConspicCourtshipAC))
courship_anovaAC <- anova(ConspicCourtshipAC)

##########
# Chromatic contrast - dS
##########
  ConspicCourtshipCC <- lmer(dS ~ sc_SVL + Population  + (1|ID), data=Courtship)
 courship_anovaCC <- anova(ConspicCourtshipCC)

 #########################################################
# Predator Context: Birds and snakes
#########################################################
 Predator <- read.table("./data/Predator_2_3.csv", 
                       header=TRUE, sep=",", dec=".", strip.white=TRUE)

@@

##########
## Achromatic Contrast - dL
##########

@@

# No support for an interaction, so can drop interaction. Tells us that predation, regardless of whether we are talking snake or bird is just low in Hawaii, otherwise, we would predict that signals would evolve to match the predatory system 
PredatorAC <- lmer(dL ~ Predator + Population + (1|ID), data = Predator) 
summary(PredatorAC)
anova_predators <- anova(PredatorAC)
##########
# Chromatic contrast - dS
##########
PredatorCC <- lmer(dS ~ Predator + Population + Predator:Population + (1|ID), data = Predator) 
summary(PredatorCC)
anova_predators_interCC <- anova(PredatorCC)

@@

#########################################################
# Local Adaptation: Testing for local adaptation
#########################################################
##################
# Social Context: Male-male competition
##################
DisplayBgrd <- read.table("./data/Display_5.csv", 
                        header=TRUE, sep=",", dec=".", strip.white=TRUE)

DisplayBgrd <- DisplayBgrd %>% 
                filter(!BodyRegion == "botflank") %>% 
                mutate(Background_pop = ifelse(Background2 == "own", Population, if_else(Background2 == "other" & Population == "Hawaii", "Kenya", "Hawaii"))) %>% 
                as.data.frame() #exclude bottom flank.
DisplayBgrd$BodyRegion <- factor(DisplayBgrd$BodyRegion) #updates levels for the variable BodyRegion

##########
# Achromatic Contrast - dL
##########
DispBgrdAC_inter <- lmer(dL ~ Population  + Background_pop + Population:Background_pop + (1|ID), data=DisplayBgrd)

DispBgrdAC <- lmer(dL ~ Population  + Background_pop  + (1|ID), data=DisplayBgrd)
summary(DispBgrdAC)
anova(DispBgrdAC_inter, DispBgrdAC)

# Robust variance esatimation to correct SE's for fixed effects given spectral curves are used multiple times for generating JNDs for each individuals data. 
clubSandwich::coef_test(DispBgrdAC, cluster = DisplayBgrd$ID, vcov =  "CR2")

DisplayBgrd$pop_back <- with(DisplayBgrd, interaction(Population, Background_pop))
DisplayBgrd_pop_back <- lmer(dL ~ pop_back + (1|ID), data = DisplayBgrd)

# df to get t-distribution, use number of lizards not data points
hypthesis_test_preppop <- glht(DisplayBgrd_pop_back, df = 69-1, 
             linfct = mcp(pop_back = c("Hawaii.Kenya  -Hawaii.Hawaii = 0")))

summary(hypthesis_test_preppop)
p_displ_AC <- as.numeric(summary(hypthesis_test_preppop)$test$pvalues)
CI_dis_AC <- as.data.frame(confint(hypthesis_test_preppop)$confint)
##########
# Chromatic Contrast - dS
##########
DispBgrdCC_inter <- lmer(dS ~ Population  + Background_pop + Population:Background_pop + (1|ID), data=DisplayBgrd)

DispBgrdCC <- lmer(dS ~ Population  + Background_pop  + (1|ID), data=DisplayBgrd)
summary(DispBgrdCC)
anova(DispBgrdCC_inter, DispBgrdCC)

# Robust variance esatimation to correct SE's for fixed effects given spectral curves are used multiple times for generating JNDs for each individuals data. 
clubSandwich::coef_test(DispBgrdCC, cluster = DisplayBgrd$ID, vcov =  "CR2")

DisplayBgrd$pop_back <- with(DisplayBgrd, interaction(Population, Background_pop))
DisplayBgrd_pop_backCC <- lmer(dS ~ pop_back + (1|ID), data = DisplayBgrd)

hypthesis_test_preppop_CC <- glht(DisplayBgrd_pop_backCC, df = 69-1, # df to get t-distribution, use number of lizards not data points
             linfct = mcp(pop_back = c("Hawaii.Kenya  -Hawaii.Hawaii = 0")))

summary(hypthesis_test_preppop_CC)
p_displ_CC <- as.numeric(summary(hypthesis_test_preppop_CC)$test$pvalues)
CI_Disp_CC <- as.data.frame(confint(hypthesis_test_preppop_CC)$confint)

###################
# Social Context: Courtship
##################
CourtshipBgrd <- read.table("./data/Courtship_5.csv", 
                        header=TRUE, sep=",", dec=".", strip.white=TRUE)

CourtshipBgrd <- CourtshipBgrd %>% 
                filter(!BodyRegion == "botflank") %>% 
                mutate(Background_pop = ifelse(Background2 == "own", Population, if_else(Background2 == "other" & Population == "Hawaii", "Kenya", "Hawaii"))) %>% 
                as.data.frame() #exclude bottom flank.
CourtshipBgrd$BodyRegion <- factor(CourtshipBgrd$BodyRegion)

##########
## Achromatic Contrast - dL
##########

CourtshipAC_inter <- lmer(dL ~ Population  + Background_pop + Population:Background_pop + (1|ID), data=CourtshipBgrd)

CourtshipAC <- lmer(dL ~ Population  + Background_pop  + (1|ID), data=CourtshipBgrd)
summary(CourtshipAC)
anova(CourtshipAC_inter, CourtshipAC)

CourtshipBgrd$pop_back <- with(CourtshipBgrd, interaction(Population, Background_pop))
CourtshipBgrd_pop_back <- lmer(dL ~ pop_back + (1|ID), data = CourtshipBgrd)

# Robust variance esatimation to correct SE's for fixed effects given spectral curves are used multiple times for generating JNDs for each individuals data. 
clubSandwich::coef_test(CourtshipAC, cluster = CourtshipBgrd$ID, vcov =  "CR2")

hypthesis_test_preppopCourtship <- glht(CourtshipBgrd_pop_back, df = 69-1, # df to get t-distribution, use number of lizards not data points
             linfct = mcp(pop_back = c("Hawaii.Kenya  -Hawaii.Hawaii = 0")))

summary(hypthesis_test_preppopCourtship)
 p_courtship_AC <- as.numeric(summary(hypthesis_test_preppopCourtship)$test$pvalues)
CI_AC_Courtship <- data.frame(confint(hypthesis_test_preppopCourtship)$confint)

##########
# Chromatic - dS
##########
CourtshipCC_inter <- lmer(dS ~ Population  + Background_pop + Population:Background_pop + (1|ID), data=CourtshipBgrd)

      CourtshipCC <- lmer(dS ~ Population  + Background_pop  + (1|ID), data=CourtshipBgrd)
      summary(CourtshipCC)
        anova(CourtshipCC)

# Test whether interaction is supported
anova(CourtshipCC_inter, CourtshipCC)

# Robust variance esatimation to correct SE's for fixed effects given spectral curves are used multiple times for generating JNDs for each individuals data. 
clubSandwich::coef_test(CourtshipCC, cluster = CourtshipBgrd$ID, vcov =  "CR2")

# Posthoc comparions
  CourtshipBgrd$pop_back <- with(CourtshipBgrd, interaction(Population, Background_pop))
CourtshipBgrd_pop_backCC <- lmer(dS ~ pop_back + (1|ID), data = CourtshipBgrd)

# Specific planned comparisons
hypthesis_test_preppopCourtshipCC <- glht(CourtshipBgrd_pop_backCC, df = 69-1, # df to get t-distribution, use number of lizards not data points
             linfct = mcp(pop_back = c("Hawaii.Kenya - Hawaii.Hawaii = 0")))

summary(hypthesis_test_preppopCourtshipCC)
p_courtship_CC <- as.numeric(summary(hypthesis_test_preppopCourtshipCC)$test$pvalues)
CI_CC_Courtship <- data.frame(confint(hypthesis_test_preppopCourtshipCC)$confint)
```

Martin J. Whiting $^1,*$, Brenden S. Holland $^2$, J. Scott Keogh$^3$, Daniel W.A.Noble$^3$, Katrina J. Rankin$^4$ and Devi M. Stuart-Fox$^4$

$^1$ Department of Biological Sciences, Macquarie University, Sydney, NSW 2109, Australia

@@

Sexual selection is expected to favour more conspicuous dymamic sexual signals in Hawaii under relaxed predation because higher predation should favour cryptic signals whereas greater conspicuousness of sexual signals should be selected in social contexts. In support of this prediction, male display colouration exhibited in social contexts (i.e., male-male contests and courtship) was more conspicuous to a conspecific in Hawaii compared with Kenya (Male-Male Contests: Acromatic contrast ($dl$); $F_{`r anovaConspicDisplayAC$NumDF[2]`,`r anovaConspicDisplayAC$DenDF[2]`}$ = `r anovaConspicDisplayAC[5][2,]`, p = `r p_value(anovaConspicDisplayAC[6][2,])`; Chromatic contrast ($dS$): $F_{`r anovaConspicDisplayCC$NumDF[2]`,`r anovaConspicDisplayCC$DenDF[2]`}$ = `r anovaConspicDisplayCC[5][2,]`, p = `r p_value(anovaConspicDisplayCC[6][2,])`; Courtship displays: Acromatic contrast ($dl$); $F_{`r courship_anovaAC$NumDF[2]`,`r courship_anovaAC$DenDF[2]`}$ = `r courship_anovaAC[5][2,]`, p = `r p_value(courship_anovaAC[6][2,])`; Chromatic contrast ($dS$): $F_{`r courship_anovaCC$NumDF[2]`,`r courship_anovaCC$DenDF[2]`}$ = `r courship_anovaCC[5][2,]`, p = `r p_value(courship_anovaCC[6][2,])`), and this was  true across all body regions measured (See Supplemental Materials, table S1). Kenyan chameleons were significantly more crypic compared to introduced Hawaiian counterparts (Acromatic Contrast between Hawaiian and Kenyan Populations, Male-male contests: $\beta$ = `r coefAIC_display`, 95% CI = `r CI_AC_display[5,1]` to  `r CI_AC_display[5,2]`, df = `r summary(ConspicDisplayAC)$coefficients[3, "df"]`, t =  `r summary(ConspicDisplayAC)$coefficients[3, "t value"]`, p = `r p_value(summary(ConspicDisplayAC)$coefficients[3, "Pr(>|t|)"])`, Courtship: $\beta$ = `r coefAIC_court`, 95% CI = `r CI_AC_court[5,1]` to  `r CI_AC_court[5,2]`, df = `r summary(ConspicCourtshipAC)$coefficients[3, "df"]`, t =  `r summary(ConspicCourtshipAC)$coefficients[3, "t value"]`, p = `r p_value(summary(ConspicCourtshipAC)$coefficients[3, "Pr(>|t|)"])`, see figure 1a & b).

@@

Local adaptation of sexual signals would result in Hawaiian chameleons being more conspicous to conspecifics in the Hawaiian environment compared to their native Kenyan environment. While it was not possible to conduct common garden experiments to provide definitive tests of local adaptation, our results support the local adaptation hypothesis given that Hawaiian chameleons were more conspicous to other chamleeons in the Hawaiian environment compared to the same chameleons in a Kenyan environment in both social contexts (figure 2; Contrast between Hawaiian lizard on Kenyan vs Hawaiian on Hawaiin background - Male-male contests: Achromatic ($dl$), $\beta$ = `r CI_dis_AC[1,1]`, 95% CI = `r CI_dis_AC[1,2]` to `r CI_dis_AC[1,3]`, p = `r p_value(p_displ_AC)`, Chromatic ($dS$) $\beta$ = `r CI_Disp_CC[1,1]`, 95% CI = `r CI_Disp_CC[1,2]` to `r CI_Disp_CC[1,3]`, p = `r p_value(p_displ_CC)`; Courtship: Achromatic ($dl$), $\beta$ = `r CI_AC_Courtship[1,1]`, 95% CI = `r CI_AC_Courtship[1,2]` to `r CI_AC_Courtship[1,3]`, p = `r p_value(p_courtship_AC)`, Chromatic ($dS$) $\beta$ = `r CI_CC_Courtship[1,1]`, 95% CI = `r CI_CC_Courtship[1,2]` to `r CI_CC_Courtship[1,3]`, p = `r p_value(p_courtship_CC)`).

@@

```{r Figure2, fig.width = 14, fig.height= 9, fig.cap= ""}
##########
# Data
##########
courtship_summary <- CourtshipBgrd %>% 
                    group_by(Population, Background_pop) %>%
                summarise( Mean_dS = mean(dS, na.rm = T), 
                             SE_dS = sd(dS)/sqrt(length(unique(ID))),
                             Upper_dS = Mean_dS + 1.96*SE_dS,
                             Lower_dS = Mean_dS - 1.96*SE_dS, 
                           Mean_dL = mean(dL, na.rm = T), 
                             SE_dL = sd(dL)/sqrt(length(unique(ID))),
                             Upper_dL = Mean_dL + 1.96*SE_dL,
                             Lower_dL = Mean_dL - 1.96*SE_dL) %>% filter(Population == "Hawaii") %>% as.data.frame() %>% mutate(Social_Context = "Courtship")

display_summary <- DisplayBgrd %>%
                group_by(Population, Background_pop) %>%
                summarise( Mean_dS = mean(dS, na.rm = T), 
                             SE_dS = sd(dS)/sqrt(length(unique(ID))),
                             Upper_dS = Mean_dS + 1.96*SE_dS,
                             Lower_dS = Mean_dS - 1.96*SE_dS, 
                           Mean_dL = mean(dL, na.rm = T), 
                             SE_dL = sd(dL)/sqrt(length(unique(ID))),
                             Upper_dL = Mean_dL + 1.96*SE_dL,
                             Lower_dL = Mean_dL - 1.96*SE_dL) %>% filter(Population == "Hawaii") %>% as.data.frame() %>% mutate(Social_Context = "Male-male contest")

summary_data_localAdap <- rbind(courtship_summary, display_summary)

##########
# Plots
##########
#Grab photos
  males <- readPNG("./photos/male_fight.png", native = TRUE)
females <- readPNG("./photos/courtship.png",  native = TRUE)

#plots
p1.2 <- ggplot(summary_data_localAdap, aes(x = Background_pop, y = Mean_dS, group = Social_Context, color = Social_Context)) +
    ylim(2.5, 6.5) + 
  geom_point(size = 3, position = position_dodge(width=0.5)) +
  geom_errorbar(aes(ymin = Lower_dS, ymax = Upper_dS), position = position_dodge(width=0.5), width = 0) + 
  geom_line(position = position_dodge(width=0.5)) + 
  scale_color_manual(values = wes_palette("Cavalcanti1")) + #Change color palette here see: https://github.com/karthik/wesanderson
  xlab("Background Environment") + 
  ylab("Chromatic contrast (JND)") +
  annotate("segment", x = 0.85, xend = 1.85, y = 6.1, yend = 6.1, colour = "black") +
  annotate("segment", x = 1.12, xend = 2.12, y = 5.7, yend = 5.7, colour = "black") + 
  annotate("text", x = 0.85+(1.85-0.85)/2,  y = 6.2, label = "NS",  size = 6) + 
  annotate("text", x = 1.12+(2.12-1.12)/2, y = 5.8, label = "NS", size = 6) + 
  theme_bw() +
  labs(colour = "Social Context") +
  theme(legend.position = c(0.28, 0.08),
    panel.grid.major = element_blank(), 
    panel.grid.minor = element_blank(),
    axis.text=element_text(size=18),
    axis.title=element_text(size=20,face="bold"),
    legend.text =element_text(size = 12),
    legend.title =element_text(size = 12, face = "bold")) +
   inset_element(males,
                left = 0.45,
                right = 0.90,
                bottom = 0.58,
                top = 0.75, ignore_tag = TRUE) + 
    inset_element(females,
                left = 0.30,
                right = 0.75,
                bottom = 0.15,
                top = 0.28, ignore_tag = TRUE)

p2.2 <- ggplot(summary_data_localAdap, aes(x = Background_pop, y = Mean_dL, group = Social_Context, color = Social_Context)) +
  ylim(15, 45) + 
  geom_point(size = 3, position = position_dodge(width=0.5)) +
  geom_errorbar(aes(ymin = Lower_dL, ymax = Upper_dL), position = position_dodge(width=0.5), width = 0) + 
  geom_line(position = position_dodge(width=0.5)) + 
  scale_color_manual(values = wes_palette("Cavalcanti1")) + #Change color palette here see: https://github.com/karthik/wesanderson
  xlab("Background Environment") + 
  ylab("Achromatic contrast (JND)") +
   annotate("segment", x = 0.90, xend = 1.90, y = 40, yend = 40, colour = "black") +
  annotate("segment", x = 1.12, xend = 2.12, y = 42, yend = 42, colour = "black") + 
  annotate("text", x = 0.9+((1.90 - 0.90)/2), y = 41, label = "**",  size = 6) + 
  annotate("text", x = 1.12+((2.12 - 1.12)/ 2), y = 43, label = "**", size = 6) + 
  theme_bw() +
  theme(legend.position = "none",
    panel.grid.major = element_blank(), 
    panel.grid.minor = element_blank(),
    axis.text=element_text(size=18),
    axis.title=element_text(size=20,face="bold"),
    legend.text =element_text(size = 12),
    legend.title =element_text(size = 12, face = "bold")) +
    inset_element(males,
                left = 0.45,
                right = 0.90,
                bottom = 0.60,
                top = 0.75, ignore_tag = TRUE) + 
    inset_element(females,
                left = 0.05,
                right = 0.50,
                bottom = 0.25,
                top = 0.38, ignore_tag = TRUE)

plot_grid(p1.2, p2.2, labels = c("A", "B"), label_size = 16,
  label_fontface = "bold", rel_widths=c(1,1))
